---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(conflicted)
library(magrittr)
```


# Part one
```{r}
df <- readxl::read_xlsx("Data_source.xlsx")
df
```

ethnicgp = ethnic group, 1 = White, 2 = Asian, 3 = West Indian, 4 = African, 5 = other
gender (male =1, female =2),
income = gross annual income before tax in 1000£
age in years
years = number of years working at this firm
commit = organisational commitment (scale 1 ~ 5)
satis = job satisfaction
autonom = job autonomy
routine = job routine
attend = attendance at meeting (yes = 1, no = 2)
skill = rated skill (unskilled, semi-skilled, fairly skilled, highly skilled, 1 ~ 4)
prody = rated productivity (very poor, poor, average, good, very good, 1 ~ 5)
qual = rated quality (very poor, poor, average, good, very good, 1 ~ 5)
absence = days of being absent in last 12 months

```{r}
dff <- df %>%  
  mutate(
    ethnicgp = as_factor(ethnicgp) %>% fct_recode("White" = "1", "Asian" = "2", "West Indian" = "3", "African" = "4", "Other" = "5"),
    gender = as_factor(gender) %>% fct_recode("Male" = "1", "Female" = "2"),
    attend = as_factor(attend) %>% fct_recode("Yes" = "1", "No" = "2"),
    skill = as_factor(skill) %>% fct_recode("Unskilled" = "1", "Semi-skilled" = "2", "Fairly skilled" = "3", "Highly skilled" = "4"),
    prody = as_factor(prody) %>% fct_recode("Very poor" = "1", "Poor" = "2", "Average" = "3", "Good" = "4", "Very good" = "5"),
    qual = as_factor(qual) %>% fct_recode("Very poor" = "1", "Poor" = "2", "Average" = "3", "Good" = "4", "Very good" = "5"),
    income = income*1000
  )
dff
```

## 1.1
### a)
Make plot of gender in Bar chart and ethnic group in pie diagram

```{r}
library(janitor)
dff %>% tabyl(gender) %>% 
  adorn_pct_formatting(affix_sign = F)
dff %>% ggplot(aes(x = gender, fill = gender)) +
  geom_bar()
```

```{r}
dff %>% 
  tabyl(ethnicgp) %>% 
  adorn_pct_formatting(affix_sign = F) -> etnias
etnias
etnias %>% as.data.frame() %>%
  ggplot(aes(x = "", y = n, fill = ethnicgp)) + 
  geom_bar(stat = "identity") +
  coord_polar("y", start = -0) + 
  theme_void()
```


### b)
Make a five number summary (max, min, median, the first and third quartiles) of Age then a box-plot

```{r}
summary(dff$age)
dff %>% ggplot(aes(y= age, x = 0)) +
  geom_boxplot() +
  xlim(-1, 1) + 
  theme(axis.text.x = element_blank(), axis.ticks.x= element_blank(), axis.x = element_blank()) 

dff %>% ggplot(aes(x = age)) +
  geom_histogram(bins = 10, alpha = 0.5) +
  geom_boxplot(aes(y = 0), width = 1) +
  ylab("frequency")

dff %>% ggplot(aes(x = age)) +
  geom_density(adjust =0.5,  alpha = 0.5) +
  geom_boxplot(aes(y = 0), width = 0.005) + 
  geom_jitter(aes(y = 0), height = 0.002, size = 0.4) +
  ylab("density")
```


### c)
Find the mean and standard deviation of income, and as well as histogram of it.
```{r}
cat("mean income = ", mean(dff$income, na.rm = T), "standard deviation = ", sd(dff$income, na.rm = T), "\n")
dff %>% ggplot(aes(income)) +
  geom_histogram(color = "#000000", fill = "#0099F8") +
  xlab("Income (£)")
dff %>% ggplot(aes(income)) +
  # https://en.wikipedia.org/wiki/Sturges%27s_rule
  geom_histogram(breaks = hist(dff$income, plot = F, breaks = "Sturges")$breaks, color = "#000000", fill = "#0099F8") +
  xlab("Income (£)")
```

## 1.2
Consider the variables income and absence.
### a)
Make scatter plot to visualize the relationship between them
```{r}
dffr <- dff %>% rename(`Days absent last 12 months` = absence, `Gross anual income (£)` = income)

dffr %>% ggplot(aes(y = `Days absent last 12 months`, x= `Gross anual income (£)`)) + 
  geom_point()
```
### b)
Find the simple regression model where income is dependent variable and rated absence is independent
variable. What is your determination coefficient?
```{r}
# TODO ask if they mean linear regression
dffr %>% lm(`Days absent last 12 months` ~ `Gross anual income (£)`, data = .) %>% summary
# dffr %>% loess(`Days absent last 12 months` ~ `Gross anual income (£)`, data = .) %>% summary
dffr %>% ggplot(aes(y = `Days absent last 12 months`, x= `Gross anual income (£)`)) + 
  geom_point() +
  geom_smooth(method = "lm")
dffr %>% ggplot(aes(y = `Days absent last 12 months`, x= `Gross anual income (£)`)) + 
  geom_point() +
  geom_smooth()
```
## 1.3
```{r}

```

