---
title: "R Notebook"
output: html_notebook
---


```{r}
library(tidyverse)
library(conflicted)

df <- readxl::read_xlsx("Data_source.xlsx")
df
```

n this part, you make use of the job survey data from the book: Quantitative data analysis with SPSS.
(the spss file jss13_ht22.sav or excel file Data_source) .
ethnicgp = ethnic group, 1 = White, 2 = Asian, 3 = West Indian, 4 = African, 5 = other
gender (male =1, female =2),
income = gross annual income before tax in 1000£
age in years
years = number of years working at this firm
commit = organisational commitment (scale 1 ~ 5)
satis = job satisfaction
autonom = job autonomy
routine = job routine
attend = attendance at meeting (yes = 1, no = 2)
skill = rated skill (unskilled, semi-skilled, fairly skilled, highly skilled, 1 ~ 4)
prody = rated productivity (very poor, poor, average, good, very good, 1 ~ 5)
qual = rated quality (very poor, poor, average, good, very good, 1 ~ 5)
absence = days of being absent in last 12 months

```{r}
# using forcats

df %<>% df
```

